A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-21 paper/refactor.tex
word-sense-document similarity formula
BUDANITSKY_2 added to bibliography

The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity. \textbf{fill me with shit from the paper}\cite{BUDANITSKY}. In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one). Path similarity was the best in the trade off between the complexity of the measure and the obtained results. This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.

@@

@@

\begin{thebibliography}{10}
\bibitem{LENIN}
Marxists Internet Archive, {\em www.marxists.org} %, No estaria pudiendo definir bien esta referencia
\bibitem{DARWIN}
M.A. Montemurro and D. H. Zanette, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
\bibitem{ENTROPIC}
M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
\bibitem{MAS-ZANETTE}
\bibitem{WORDNET}
George A. Miller, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
\bibitem{LESK}
M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.
\bibitem{BUDANITSKY}
Evaluating WordNet-based Measures of Lexical Semantic Relatedness
http://aclweb.org/anthology//J/J06/J06-1003.pdf
\end{thebibliography}
\end{article}
\end{document}

>>>>

The similarities defined in the nltk-api are the following: Path similarity, Leacock-Chodorow similarity, Resnik similarity, Jiang-Conrath similarity and Lin similarity. \textbf{fill me with shit from the paper}\cite{BUDANITSKY}\cite{BUDANITSKY_2}. In this project, we present the results measured with path similarity because the idea is to present a proof of concept of a representation for documents (and not a 'productive' one). Path similarity was the best in the trade off between the complexity of the measure and the obtained results. This similarity represents the distance between two nodes in Wordnet based on the shortest path that connects the senses in the is-a (hypernym/hypnoym) taxonomy.

@@

Finally, we define the similarity between a document and a word-sense as follows:

\begin{equation}
  similarity(w, T) = max(path\_similarity(w, top\_senses_n(T)))
\end{equation}

@@

\begin{thebibliography}{10}
\bibitem{LENIN}
Marxists Internet Archive, {\em www.marxists.org} %, No estaria pudiendo definir bien esta referencia
\bibitem{DARWIN}
M.A. Montemurro and D. H. Zanette, {\em The statistics of meaning: Darwin, Gibbon and Moby Dick}, Significance, Dec. 2009, 165-169.
\bibitem{ENTROPIC}
M.A. Montemurro and D. H. Zanette, {\em Entropic analysis of the role of words in literary texts}, Adv. Complex Systems 5, September 27th 2001
\bibitem{MAS-ZANETTE}
\bibitem{WORDNET}
George A. Miller, {\em WordNet: A Lexical Database for English }, COMMUNICATIONS OF THE ACM November 1995/Vol. 38, No. 11
\bibitem{LESK}
M. Lesk. Automatic sense disambiguation using machine readable dictionaries: How to tell a pine cone from a ice cream cone. In Proceedings of SIGDOC ’86, 1986.
\bibitem{BUDANITSKY}
Evaluating WordNet-based Measures of Lexical Semantic Relatedness
http://aclweb.org/anthology//J/J06/J06-1003.pdf
\bibitem{BUDANITSKY_2}
Semantic distance in WordNet: An experimental, application-oriented evaluation of five measures
ftp://learning.cs.utoronto.ca/pub/gh/Budanitsky+Hirst-2001.pdf
\end{thebibliography}
\end{article}
\end{document}
